### 2022-03-29 manuscript.tex
picturessmaller [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/330b3032e45afe681efd66fc81301108e295a421.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/330b3032e45afe681efd66fc81301108e295a421/checks
https://github.com/scherzerthesis/thesis/actions/runs/2060954723

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/a119b0356ed253d1329bba93ed47dab071e57182/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/a119b0356ed253d1329bba93ed47dab071e57182}{scherzerthesis/thesis@a119b03}
on March 29, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/330b3032e45afe681efd66fc81301108e295a421/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/330b3032e45afe681efd66fc81301108e295a421}{scherzerthesis/thesis@330b303}
on March 29, 2022.
